\hspace{0.5in}
Introducing a new project ”laptop selection and price prediction”. The main aim
of this project selecting of the best laptops based on financial position with the best
features. After evaluation of technology, we all use laptops to complete our tasks
very fastly, effectively and accurately. Nowadays laptop plays a crucial role in every
field like education, manufacturing, the service sector etc..to achieve this, we took the
dataset from the Kaggle website the dataset mainly contains information about the
1000 laptops on India’s E-Commerence platform like Flipkart. The dataset contains
technical features like Ram, Preprocessor type, Hard disk, display resolution, storage
info, number of reviewers, number of ratings, etc. It also provides the image link
related to the particular laptop.
This project is built using Data science and machine learning models. we use
Python libraries like Numpy, Scipy, pandas, Scikit-Learn and Matplotlib for the anal-
ysis of the data to get desired output. In this project, we mainly compare all features
of different laptops and select the best laptop among all and also predict the price of
the laptop based on features and compare it with the given price.
Nowadays most of the people suffer in decision-making in the selection of the best
laptop for their needs. This project will help them and it also helps businessmen in
decision-making in which laptop production is to be increased to get more profits.
Based on reviews, this project leads to the manufacturing of new laptop based on
the requirements of consumers.


 
